The Exoplanet Orbit Database \textsc{II}: updates for 2014

### 2014-03-25 draft/references.tex
Revision 1

@@

@@

>>>>

\bibitem[Lagrange et al.(2009)]{Lagrange2009} Lagrange, A.-M., Gratadour, D., Chauvin, G., et al.\ 2009, \aap, 493, L21 %beta Pic b, imaging planet with I measured

@@

\bibitem[Mahadevan et al.(2012)]{Mahadevan2012} Mahadevan, S., 
Ramsey, L., Bender, C., et al.\ 2012, \procspie, 8446, %HPF

@@

\bibitem[Moutou et al.(2011)]{Moutou2011} Moutou, C., D{\'{\i}}az, R.~F., Udry, S., et al.\ 2011, \aap, 533, A113  %Lambda example
